Improving Code Completion in Pharo\\Using N-gram Language Models

### 2020-02-19 ACM/abstract.tex
Fixed a typo

\oz{Don't write the title of every paper, simply cite them and titles will appear in references} \oz{My work was inspired by } The \oz{\sout{famous}} paper "On The Naturalness of Software" \oz{\sout{( by}} Hindle et al.\oz{\sout{)}} \cite{Hind12a} \oz{\sout{served as a sort of catalyst for the following research, applying statistical models to Pharo}}. There, as well as in \oz{\sout{"On the localness of software" (Tu et al.), "Code completion with statistical language models" (Raychev et al.), "Are deep neural networks the best choice for modeling source code?" (Hellendoorn et al.) and "Code completion with neural attention and pointer networks" (Li et al.)}}\cite{Tu14a,Rayc14a,Hell17a,Li17a}, the structural information is not taken into consideration and the problem of improving code completion is reduced to a natural language processing problem, where predicting the next token is treated as predicting the next word in a sentence.

>>>>

\oz{Don't write the title of every paper, simply cite them and titles will appear in references} \oz{My work was inspired by } The \oz{\sout{famous}} paper "On The Naturalness of Software" \oz{\sout{( }by} Hindle et al.\oz{\sout{)}} \cite{Hind12a} \oz{\sout{served as a sort of catalyst for the following research, applying statistical models to Pharo}}. There, as well as in \oz{\sout{"On the localness of software" (Tu et al.), "Code completion with statistical language models" (Raychev et al.), "Are deep neural networks the best choice for modeling source code?" (Hellendoorn et al.) and "Code completion with neural attention and pointer networks" (Li et al.)}}\cite{Tu14a,Rayc14a,Hell17a,Li17a}, the structural information is not taken into consideration and the problem of improving code completion is reduced to a natural language processing problem, where predicting the next token is treated as predicting the next word in a sentence.
